Evaluating infectious disease forecasts with allocation scoring rules

### 2023-07-11 alloscore_manuscript/allocation.tex
1st attempt at integrating allocation score intro... we probably don't want subsections though

As described above, there exists both a rich literature on outbreak forecast evaluation and an emerging body of work on turning forecasts into resource allocation decisions. 
However, there has been far less attention paid (no papers that we could identify) to exploring whether standard forecast accuracy metrics are sufficient for evaluating forecasts that are used to make allocation decisions.
In this work, we address the gap between the ways in which infectious disease forecasts have been used to support public health policy and the ways in which they have traditionally been evaluated. 
Specifically, we define a new forecast scoring rule --the {\em allocation score}-- that explicitly evaluates forecasts based on how accurate their implied allocations would turn out to be.
This stands in contrast to standard evaluation metrics that evaluate the accuracy of a forecast relative to the surveillance data being forecasted.

@@

@@

>>>>

@@

As described above, there exists both a rich literature on outbreak forecast evaluation and an emerging body of work on turning forecasts into resource allocation decisions. 
However, we have not found literature exploring whether standard forecast accuracy metrics are sufficient for evaluating how well forecasts support allocation decisions.
We hope to begin in this work to fill this gap between the ways in which infectious disease forecasts have been used to support public health policy and the ways in which they have traditionally been evaluated. 
To this end, we define a new forecast scoring rule --- the {\em allocation score} --- that explicitly evaluates forecasts based on how beneficial their implied allocations would turn out to be rather than some standard statisitical measure of their accuracy relative to the surveillance data being forecasted.

@@

\subsection{Organization}
